\documentclass[10pt]{article}

\usepackage[a4paper, total={7in, 10in}]{geometry} % define page size
\usepackage{hyperref} % for linked in ref
\usepackage{array, xcolor} % for colour
\usepackage{eurosym} % for the euro symbol
\usepackage{enumitem} % http://ctan.org/pkg/enumitem
\usepackage{longtable} % multi page table
\usepackage{fontawesome} % for symbols

\definecolor{lightgray}{gray}{0.8}

\newcolumntype{L}{>{\raggedleft}p{0.14\textwidth}}
\newcolumntype{R}{p{0.8\textwidth}}
\newcommand\VRule{\color{lightgray}\vrule width 0.5pt}

\title{\bfseries\Huge Natalie Branston}

\date{}
\author{}

\begin{document}

\maketitle \vspace{-7em}

% Contact Details
\section*{}
\faPhone \quad 07837 484375\\
\faEnvelope \quad nataliejadebranston@hotmail.co.uk\\
\faMapMarker \quad SA1 7LJ

\section*{Skills}
\begin{itemize} \setlength\itemsep{-0.25em}
	\item One to one support for individual children
	\item Teaching classes unsupervised while covering PPA
	\item TA support in multiple classroom contexts
	\item Supporting ASD/ADHD children ages 3-13
\end{itemize}

% experience
\section*{Experience}
\begin{longtable}{L!{\VRule}R}

% Cwm Glas TA
{\bf Cwm Glas Primary}\\
Sep 2012--present\\
&{\bf Teaching Assistant}\newline
Since Nov 2021, I have been qualified as an HLTA.

\vspace{-3mm}
\paragraph{Responsibilities:}
\begin{itemize}[noitemsep,topsep=0pt]
    \item Assisting the teacher with preparing for daily tasks and activities.
    \item Covered PPA time and led classroom activities unsupervised.
    \item Promoting and encouraging children's development within the school curriculum through supporting the children and planning and implementing my own activities and lessons.
    \item Supervising the children at all times, and being aware of health and safety, whilst in the school environment and on school trips.
    \item Worked 1:1 for 4 years with a child that has ASD.
\end{itemize}
\\

% Mark warner act leader
{\bf Mark Warner Holidays}\\
July 2019--Sep 2019\\
&{\bf Children's Activity Leader}\newline

\vspace{-3mm}
\paragraph{Responsibilities:}
\begin{itemize}[noitemsep,topsep=0pt]
    \item Providing fun, age appropriate activities.
    \item Assisting children during water sport activities.
    \item Babysitting in the evenings.
\end{itemize}
\\

% sports direct
{\bf Sports Direct}\\
Nov 2012--2016\\
&{\bf Sales Assistant}\newline
Providing customers with a good quality service.

\vspace{-3mm}
\paragraph{Responsibilities:}
\begin{itemize}[noitemsep,topsep=0pt]
    \item Interacting with new people on a daily basis.
    \item Working within a team to complete all tasks set.
    \item Training new staff and leading a shop floor to complete all tasks set by the shop manager.
\end{itemize}
\end{longtable}

% Education
\section*{Education}

\begin{longtable}{L!{\VRule}R}

% HLTA
{\bf Learning Association}\\
November 2021\\
    &{\bf Higher Level Teaching Assistant (HLTA)}\newline
\\

% Gower college
{\bf Children's Care Learning and Development}\\
2012--2014\\
    &{\bf BTEC Level 3}\newline
\\

\end{longtable}

% personal details
\section*{Personal Details}
\begin{itemize}[noitemsep,topsep=0pt]
    \item Genuine passion for children and teaching
    \item Energetic and enthusiasic personality with an eagerness to learn and take on challenges
	\item Full UK driving licence.
\end{itemize}

\end{document}
